%-------------------------
% Priyansh Agrahari 2024
% Reference: https://www.overleaf.com/project/61e5a2e4ac7f2fba758087f0
%------------------------

\documentclass[a4,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.75in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-8pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\sectionEndVspace}{-22pt}
\newcommand{\projectListItemVspace}{-20pt}



\begin{document}

\begin{center}
    {\Huge \scshape Priyansh Agrahari} \\ \vspace{1pt}
    International Institute of Information Technology, Bangalore \\ \vspace{1pt}
    \small \href{tel:+919179918909}{\raisebox{-0.2\height}\faPhone\  \underline{9179918909}} ~ \href{mailto:priyansh.agrahari@iiitb.ac.in}{\raisebox{-0.2\height}\faEnvelope\  \underline{priyansh.agrahari@iiitb.ac.in}} ~
    \href{https://linkedin.com/in/priyansh-agr/}{\raisebox{-0.2\height}\faLinkedin\ \underline{in/priyansh-agr}}  ~
    \href{https://github.com/r3dacted42/}{\raisebox{-0.2\height}\faGithub\ \underline{r3dacted42}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International Institute of Information Technology, Bangalore}{July 2024 -- June 2026}
      {Master of Technology in Computer Science}{3.18}
    \vspace{-4pt}
    \resumeSubheading
      {Indian Institute of Information Technology, Raichur}{Dec 2020 -- May 2024}
      {Bachelor of Technology in Computer Science}{3.36}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Rolls-Royce India Pvt. Ltd.}{Jan 2026 -- Current (till June 2026)}
      {Apprentice}{Bengaluru}
      \resumeItemListStart
        \resumeItem{Delivered 2 Power Apps dedicated to employee social and physical well-being, leveraging the full Power Platform stack.}
        \resumeItem{Contributed to full-stack development and maintenance using Angular, performing bug fixes and QA testing.}
      \resumeItemListEnd
      \vspace{-4pt}
    
    \resumeSubheading
      {Oracle Cerner Healthcare Solutions India Pvt. Ltd.}{May 2025 -- July 2025}
      {Project Intern}{Bengaluru}
      \resumeItemListStart
        \resumeItem{Digitized 20 resources of the RAI spec into dynamic web forms, streamlining clinical data entry for the LTC EHR React app.}
        \resumeItem{Upskilled in Oracle's core tech stack: Oracle Cloud, OJET, Micronaut, and Visual Builder, for future projects.}
      \resumeItemListEnd
      \vspace{-4pt}
  
    \resumeSubheading
      {GoLive Games Studios Pvt. Ltd.}{May 2022 -- May 2023}
      {Game Programmer Intern}{WFH}
      \resumeItemListStart
        \resumeItem{Developed efficient C\# scripts using the Unity API to add features and fix bugs in 2D and 3D early-stage to live projects.}
        \resumeItem{Reduced load times and latency by 70\% on an Android mobile game by optimizing load-up sequence and caching.}
      \resumeItemListEnd
      
    \resumeSubHeadingListEnd
\vspace{\sectionEndVspace}


%-----------COURSE PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
      {\textbf{Static C++ Null Pointer Analyzer} $|$ \emph{C++, Clang, GCP, Docker} $|$ \href{https://github.com/r3dacted42/static-null-analyzer}{\faLink\ Repo} \ \href{https://static-null-analyzer-50533719506.asia-south2.run.app}{\faLink\ Live} }{Sep 2025 -- Dec 2025}
      \resumeItemListStart
        \resumeItem{Engineered a C++ static analyzer that maps Clang ASTs to custom CFGs to detect null pointer risks, supporting various C++ constructs, including a web app with a code-editor and GraphViz-based visualization for the CFG.}
        \resumeItem{Containerized the analyzer and Web App into a multi-stage Docker image deployed on Google Cloud Run (GCP).}
      \resumeItemListEnd 
      \vspace{\projectListItemVspace}
    
      \resumeProjectHeading
      {\textbf{Sparrow VPS} $|$ \emph{Kubernetes, Docker, Gin (Go), FastAPI, Vue} $|$ \href{https://github.com/r3dacted42/sparrow-vps}{\faLink\ Repo}}{Apr 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{Designed a scalable cloud-native Virtual Private Server to ease the containerization and deployment process of projects.}
        \resumeItem{Implemented 6 core services for managing the application life-cycle, including repository analysis for stack detection, automated image builds, efficient deployment and monitoring.}
      \resumeItemListEnd 
      \vspace{\projectListItemVspace}
    
      \resumeProjectHeading
      {\textbf{Concurrent TUI Banking System} $|$ \emph{C, Ncurses, pthread} $|$ \href{https://github.com/r3dacted42/bank-mgmt-sys}{\faLink\ Repo}}{Sep 2024 -- Oct 2024}
      \resumeItemListStart
        \resumeItem{Developed a high-concurrency system in C, using socket programming \& multi-threading to support up to 512 connections.}
        \resumeItem{Ensured ease of use, data integrity and security by implementing an Ncurses TUI, single-session per user, record-level file locking for persistent storage, and RBAC with bcrypt password hashing.}
      \resumeItemListEnd 
      \vspace{\projectListItemVspace}

      \resumeProjectHeading
      {\textbf{EmpERP (Full Stack)} $|$ \emph{React, Spring Boot, MySQL} $|$ \href{https://github.com/r3dacted42/EmpERP}{\faLink\ Repo}}{Aug 2024 -- Oct 2024}
      \resumeItemListStart
        \resumeItem{Developed a full-stack app with Spring Boot, React, and MySQL, featuring RESTful APIs with JWT for security.}
        \resumeItem{Integrated core features like employee onboarding, department management, and salary administration.}
        % \resumeItem{Reduced API response times by 20\% by adhering to the MVC architecture and providing clear API documentation, ensuring a maintainable and scalable application.}
      \resumeItemListEnd
      \vspace{\projectListItemVspace}
          
%     \resumeSubHeadingListEnd
% \vspace{\sectionEndVspace}


%-----------PERSONAL PROJECTS-----------
% \section{Personal Projects}
%     \vspace{-5pt}
%     \resumeSubHeadingListStart
    
      % \resumeProjectHeading
      % {\textbf{Tic Tac Toe (Web App)} $|$ \emph{Phaser, Pusher, Express.js} $|$ \href{https://github.com/r3dacted42/tic-tac-toe}{\faLink\ Repo} $|$ \href{https://tic-tac-toe-chi-liart.vercel.app/}{\textbf{Deployment}}}{Oct 2023 -- Jan 2024}
      % \resumeItemListStart
      %   \resumeItem{Deployed a real-time, multi-player game utilizing Phaser for frontend rendering and Pusher for communication.}
      %   \resumeItem{Increased engagement by 100\% using social features such as shared room codes for gameplay and in-game chat.}
      % \resumeItemListEnd 
      % \vspace{\projectListItemVspace}
  
      \resumeProjectHeading
      {\textbf{IIITR Connect (Attendance App)} $|$ \emph{Flutter, OpenCV, FastAPI, PostgreSQL} $|$ \href{https://github.com/r3dacted42/iiitr_connect}{\faLink\ Repo FE} \ \href{https://github.com/r3dacted42/iiitr_connect_backend}{\faLink\ Repo BE}}{Aug 2023 -- Dec 2023}
      \resumeItemListStart
        \resumeItem{Saved $\sim$15 minutes per class session by automating student attendance with a facial recognition system.}
        \resumeItem{Designed and built a cross-platform Flutter mobile app with a secure authority-based RESTful API backend using FastAPI.}
      \resumeItemListEnd 
      % \vspace{\projectListItemVspace}

      % \resumeProjectHeading
      % {\textbf{SkelRunner (Android Mobile Game)} $|$ \emph{Unity, C\#} $|$ \href{https://play.google.com/store/apps/details?id=com.r3dacted42.skelrunner}{\textbf{Google Play}}}{Sep 2022 - Mar 2023}
      % \resumeItemListStart
      %   \resumeItem{Developed an infinite runner game for Android using Unity and C\#.}
      %   \resumeItem{Implemented engaging gameplay mechanics, rich audio-visual effects, and an ad-monetization strategy.}
      % \resumeItemListEnd 
          
    \resumeSubHeadingListEnd
\vspace{\sectionEndVspace}


%-----------MENTORSHIP/TEACHING ASSISTANCE-----------
\section{Mentorship}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Teaching Assistant}{Jan 2022 -- June 2022}{Intro to Data Structures, Programming}
      {IIIT Raichur}
      \resumeItemListStart
        \resumeItem{Held 20+ interactive teaching sessions with students on various topics in data structures and C/C++ programming.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{\sectionEndVspace}


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Technologies}{: Docker, Kubernetes, Three.JS, Flutter, Qt, Spring, React, FastAPI, PostgreSQL, Unreal, Unity } \\
     \textbf{Languages}{: C/C++, Dart, Go, C\#, Java, Bash, Typescript/JavaScript, PHP, HTML/CSS, Python } \\
    }}
 \end{itemize}
 \vspace{\sectionEndVspace}


%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
        \begin{multicols}{4}
            \begin{itemize}[leftmargin=0.2in, itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Software Methodology
                \item Algorithms Analysis
                \item Database Management
                \item Artificial Intelligence
                \item Internet Technology
                \item Systems Programming
                \item Computer Architecture
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}

\end{document}
